Systematic studies of correlations between different order flow harmonics in Pb-Pb collisions at $\sqrt{s_{NN}}$ = 2.76 TeV

### 2018-01-15 Alice_Authorlist_2017-Aug-21.tex
author list USA

\section*{Affiliation notes}
\renewcommand\theenumi{\roman{enumi}}
\begin{Authlist}
\item \Adef{org*}Deceased
\item \Adef{orgI}Dipartimento DET del Politecnico di Torino, Turin, Italy
\item \Adef{orgII}Georgia State University, Atlanta, Georgia, United States
\item \Adef{orgIII}M.V. Lomonosov Moscow State University, D.V. Skobeltsyn Institute of Nuclear, Physics, Moscow, Russia
\item \Adef{orgIV}Department of Applied Physics, Aligarh Muslim University, Aligarh, India
\item \Adef{orgV}Institute of Theoretical Physics, University of Wroclaw, Poland
\end{Authlist}

@@

\item \Idef{org6}California Polytechnic State University, San Luis Obispo, California, United States

@@

\item \Idef{org12}Chicago State University, Chicago, Illinois, United States

@@

\item \Idef{org16}Department of Physics, Ohio State University, Columbus, Ohio, United States

@@

\item \Idef{org81}Lawrence Berkeley National Laboratory, Berkeley, California, United States

@@

\item \Idef{org94}Oak Ridge National Laboratory, Oak Ridge, Tennessee, United States

@@

\item \Idef{org96}Physics Department, Creighton University, Omaha, Nebraska, United States

@@

\item \Idef{org105}Purdue University, West Lafayette, Indiana, United States

@@

\item \Idef{org119}The University of Texas at Austin, Physics Department, Austin, Texas, United States

@@

\item \Idef{org124}University of Houston, Houston, Texas, United States

@@

\item \Idef{org127}University of Tennessee, Knoxville, Tennessee, United States

@@

\item \Idef{org139}Wayne State University, Detroit, Michigan, United States

@@

\item \Idef{org141}Yale University, New Haven, Connecticut, United States

>>>>

\section*{Affiliation notes}
\renewcommand\theenumi{\roman{enumi}}
\begin{Authlist}
\item \Adef{org*}Deceased
\item \Adef{orgI}Dipartimento DET del Politecnico di Torino, Turin, Italy
\item \Adef{orgII}Georgia State University, Atlanta, Georgia, USA
\item \Adef{orgIII}M.V. Lomonosov Moscow State University, D.V. Skobeltsyn Institute of Nuclear, Physics, Moscow, Russia
\item \Adef{orgIV}Department of Applied Physics, Aligarh Muslim University, Aligarh, India
\item \Adef{orgV}Institute of Theoretical Physics, University of Wroclaw, Poland
\end{Authlist}

@@

\item \Idef{org6}California Polytechnic State University, San Luis Obispo, California, USA

@@

\item \Idef{org12}Chicago State University, Chicago, Illinois, USA

@@

\item \Idef{org16}Department of Physics, Ohio State University, Columbus, Ohio, USA

@@

\item \Idef{org81}Lawrence Berkeley National Laboratory, Berkeley, California, USA

@@

\item \Idef{org94}Oak Ridge National Laboratory, Oak Ridge, Tennessee, USA

@@

\item \Idef{org96}Physics Department, Creighton University, Omaha, Nebraska, USA

@@

\item \Idef{org105}Purdue University, West Lafayette, Indiana, USA

@@

\item \Idef{org119}The University of Texas at Austin, Physics Department, Austin, Texas, USA

@@

\item \Idef{org124}University of Houston, Houston, Texas, USA

@@

\item \Idef{org127}University of Tennessee, Knoxville, Tennessee, USA

@@

\item \Idef{org139}Wayne State University, Detroit, Michigan, USA

@@

\item \Idef{org141}Yale University, New Haven, Connecticut, USA
